Uncovering underlying high-level musical content in the time domain \\ \small Leveraging self-supervised deep neural networks, inductive bias, and aural skills to learn deep audio embeddings with applications to boundary detection tasks

### 2023-07-04 discussion/discussion.tex
Updates from Overleaf

While not outperforming state-of-the-art existing baselines and in contrast to similar research findings such \cite{deepfeaturesegment, SalamonDeepSegmentation}, our musically-informed technique has significant potential for boundary detection tasks given its overall performance improvement alongside the training set enlargement. Most likely, so does for nearly all MIR downstream tasks that are not purely sonic-based.

The questions of whether such general-purpose audio representation can mimic human hearing \cite{Li2023MERT:Training, Turian2022HEAR:Representations} or whether these do decode underlying high-level musical content effectively remain scientifically unanswered given the lack of evaluation in that regard. That is a "thorn in our side" that we will pursue.

@@

While whether our model decodes underlying high-level musical content effectively remains scientifically unanswered, the outstanding performance in precision metric

>>>>

While our musically-informed technique does not yet outperform the existing state-of-the-art baselines \cite{deepfeaturesegment, SalamonDeepSegmentation}, it exhibits significant potential in boundary detection tasks, particularly when expanding the training set. The improvement we've observed between datasets is noteworthy, and when compared with two of the acoustic features, our results are highly competitive. We've also managed to circumvent the typical issues associated with dataset enlargements, such as the need for extensive supervision or human annotation, which gives our method an edge in terms of practicality and scalability effectively turning what is usually seen as an expensive hurdle into a much more manageable task.

@@

Whether our model effectively decodes underlying high-level musical content remains open to scientific investigation. It's plausible that our technique possesses significant potential for nearly all content-based MIR downstream tasks, given its intention to be both sound-agnostic and content-sensitive. Queries persist about whether such a general-purpose audio representation can mimic human hearing \cite{Li2023MERT:Training, Turian2022HEAR:Representations}, or if it can accurately decode high-level musical content. Such questions remain unresolved due to the current lack of evaluative measures. This represents a 'thorn in our side' that we intend to address in future research.

### 2023-07-04 results/results.tex
Updates from Overleaf

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/images/first results.png}
    \caption{Caption}
    \label{fig:boxplotmetrics}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/images/f-measure.png}
    \caption{Caption}
    \label{fig:boxplotfmeasure}
\end{figure}

>>>>

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/images/boxplot.png}
    \caption[Metric comparison for different audio features.]{\small{Boxplot visual comparison of different features' average precision, recall, and f-measure. Sliding windowed segments across the audio signal input signal is 4 seconds.}}
    \label{fig:boxplotmetrics}
\end{figure}

### 2023-07-04 results/subsections/tables.tex
Updates from Overleaf

\newsavebox\embeddioaSF
\begin{lrbox}{\embeddioaSF}
   $\begin{aligned}
     0.228 & \quad 0.171 & \quad 0.185
    \end{aligned} $
\end{lrbox}

\newsavebox\embeddioaFoote
\begin{lrbox}{\embeddioaFoote}
   $\begin{aligned}
      & \quad  & \quad 
    \end{aligned} $
\end{lrbox}

\newsavebox\embeddioaCNMF
\begin{lrbox}{\embeddioaCNMF}
   $\begin{aligned}
      & \quad  & \quad 
    \end{aligned} $
\end{lrbox}

@@

\begin{table}
  \centering
  \begin{adjustbox}{width=\textwidth}
  \begin{threeparttable}
    \begin{tabular}{c|l|c|c|c} 
\toprule
     \multicolumn{2}{c|}{\textbf{Training dataset} and \textbf{Feature}}  & \multicolumn{1}{c}{\textbf{SF}} & \multicolumn{1}{c}{\textbf{Foote}} & \multicolumn{1}{c}{\textbf{CNMF}} 
     \\ \midrule 
    \multirow{5}{*}{}&
        \multirow{1}{*}{PCP} & \usebox{\pcpSF} & \usebox{\pcpFoote} & \usebox{\pcpCNMF} \\\cline{2-5}
        & \multirow{1}{*}{Tonnetz} & \usebox{\tonnetzSF} & \usebox{\tonnetzFoote} & \usebox{\tonnetzCNMF} \\\cline{2-5} 
        & \multirow{1}{*}{CQT} & \usebox{\cqtSF} & \usebox{\cqtFoote} & \usebox{\cqtCNMF} \\\cline{1-5} 
    \multirow{1}{*}{GTZAN \cite{GTZAN}}& 
        \multirow{1}{*}{\textbf{Embeddiogram}} & \usebox{\embeddioaSF} & \usebox{\embeddioaFoote} & \usebox{\embeddioaCNMF} \\\cline{1-5} 
    \multirow{1}{*}{MSD \cite{MSD}}& 
        \multirow{1}{*}{\textbf{Embeddiogram}} & \usebox{\embeddiobSF} & \usebox{\embeddiobFoote} & \usebox{\embeddiobCNMF} \\\bottomrule
    \end{tabular}
    \caption[Metric comparison: audio features and segmentation algorithms]{Comparison of precision, recall, and f-measure for different features using the Structural Feature (SF)\cite{sf}, Checkerboard Kernel (Foote) \cite{Foote2000AutomaticNovelty}, and Convex Non-negative Matrix Factorization (CNMF) \cite{NietoCONVEXIDENTIFICATION} algorithms on the SALAMI dataset. Sliding windowed segments across the audio signal input signal is 4 seconds long.}\label{ta:results}
  \end{threeparttable}
  \end{adjustbox}
\end{table}

@@

\begin{table}[h]
\centering
\small
\begin{tabularx}{\textwidth}{>{\raggedright\arraybackslash}p{4.5cm}XXXXX}
\toprule
\thead{\centering\textbf{Authors [Ref], Year}} & \thead{\centering\textbf{Input}} & \thead{\centering\textbf{Method}} & \thead{\centering\textbf{F-measure}} \\
\midrule
\addlinespace
Turnbull et al. \cite{Turnbull2007ABOOSTING}, 2007 & MFCCs, chromas, spectrogram & Boosted Decision Stump  & 0.378 \\
\addlinespace
Kaiser et al. \cite{27}, 2012 & SSM & Novelty measure  & 0.286 \\
\addlinespace
McFee \& Ellis \cite{20}, 2013 & MLS & Fisher’s Linear Discriminant  & 0.317 \\
\addlinespace
Nieto \& Bello \cite{28}, 2014 & MFCCs, chromas & Checkerboard-like kernel  & 0.299 \\
\addlinespace
Cannam et al. \cite{29}, 2015 & Timbre-type histograms & HMM  & 0.213 \\
\addlinespace
Nieto \cite{30}, 2016 & Constant-Q Transform Spectrogram & Linear Discriminant Analysis  & 0.299 \\
\addlinespace
Cannam et al. \cite{29}, 2017 & Timbre-type histograms & HMM  & 0.212 \\
\addlinespace
Sargent et al. \cite{34}, 2011 & MFCCs, chromas & Viterbi  & 0.356 \\
\addlinespace
Ullrich et. al \cite{22}, 2014 & MLS & CNN  & 0.465 \\
\addlinespace
Grill \& Schlüter \cite{4}, 2015 & MLS, SSLMs & CNN  & 0.523 \\
\addlinespace
Grill \& Schlüter \cite{Grill2015MusicAnnotations}, 2015 & MLS, PCPs, SSLMs & CNN  & 0.508 \\
\addlinespace
Hadria \& Peeterss \cite{35}, 2017 & MLS, SSLMs & CNN  & 0.291 \\
\addlinespace
\cite{deepfeaturesegment}, 2019 & CQT & CNN  & \textbf{0.535} ± 0.15 \\
\addlinespace
Ours, 2023 & Raw waveforms & CNN  & 0.288 \\
\bottomrule
\end{tabularx}
\caption[Baseline. State-of-the-art table.]{\small{Previous studies' boundary detection f-measure results using unsupervised methods for a 0.5s time-window tolerance. Only the top-performing algorithm for each year on the SALAMI dataset is displayed. This table has been extended from \cite{Hernandez-Olivan2021MusicFeatures}.}}
\label{tab:comparison_table}
\end{table}

>>>>

\begin{table}[h]
\centering
\small
\begin{tabularx}{\textwidth}{>{\centering\arraybackslash}p{4.5cm}>{\centering\arraybackslash}X>{\centering\arraybackslash}X>{\centering\arraybackslash}X}
\toprule
\textbf{Training dataset [Ref]}  & \textbf{Precision} & \textbf{Recall} & \textbf{F-measure} \\
\midrule
\addlinespace
GTZAN \cite{GTZAN} & 0.228 & 0.171 & 0.185 \\
\addlinespace
MSD \cite{MSD} &  \textbf{0.333} &  \textbf{0.280} & \textbf{0.288} \\
\addlinespace
\bottomrule
\end{tabularx}
\caption[Caption]{\small{Comparison of precision, recall, and f-measure for GTZAN-trained versus MSD-trained embeddiograms on SALAMI dataset computed using the Structural Feature (SF)\cite{sf} algorithm.}}
\label{tab:comparison_table}
\end{table}

@@

\begin{table}
  \centering
  \begin{adjustbox}{width=\textwidth}
  \begin{threeparttable}
    \begin{tabular}{c|c|c|c|c} 
\toprule
     \textbf{Feature} & \textbf{SF} & \textbf{Foote} & \textbf{CNMF} 
     \\ \midrule 
     PCP & \usebox{\pcpSF} & \usebox{\pcpFoote} & \usebox{\pcpCNMF} \\\hline
     Tonnetz & \usebox{\tonnetzSF} & \usebox{\tonnetzFoote} & \usebox{\tonnetzCNMF} \\\hline
     CQT & \usebox{\cqtSF} & \usebox{\cqtFoote} & \usebox{\cqtCNMF} \\\hline
     Embeddiogram & \usebox{\embeddiobSF} & \usebox{\embeddiobFoote} & \usebox{\embeddiobCNMF} \\
     \bottomrule
    \end{tabular}
    \caption[Metric comparison: audio features and segmentation algorithms]{Comparison of precision (left column), recall (middle column), and f-measure (right column) metrics for different features using the Structural Feature (SF)\cite{sf}, Checkerboard-like Kernel (Foote) \cite{Foote2000AutomaticNovelty}, and Convex Non-negative Matrix Factorization (CNMF) \cite{NietoCONVEXIDENTIFICATION} algorithms on the SALAMI dataset. The sliding windowed segments across the input signal is 4 seconds long.}\label{ta:results}
  \end{threeparttable}
  \end{adjustbox}
\end{table}

@@

\begin{table}[h]
\centering
\small
\begin{tabularx}{\textwidth}{>{\centering\arraybackslash}p{4.5cm}XXXX}
\toprule
\thead{\textbf{Authors [Ref], Year}} & \thead{\textbf{Input}} & \thead{\textbf{Method}} & \thead{\textbf{F-measure}} \\
\midrule
Turnbull et al. \cite{Turnbull2007ABOOSTING}, 2007 & MFCCs, chromas, spectrogram & Boosted Decision Stump  & 0.378 \\
\addlinespace
Kaiser et al. \cite{27}, 2012 & SSM & Novelty measure  & 0.286 \\
\addlinespace
McFee \& Ellis \cite{20}, 2013 & MLS & Fisher’s Linear Discriminant  & 0.317 \\
\addlinespace
Nieto \& Bello \cite{28}, 2014 & MFCCs, chromas & Checkerboard-like kernel  & 0.299 \\
\addlinespace
Cannam et al. \cite{29}, 2015 & Timbre-type histograms & HMM  & 0.213 \\
\addlinespace
Nieto \cite{30}, 2016 & CQT Spectrogram & Linear Discriminant Analysis  & 0.299 \\
\addlinespace
Cannam et al. \cite{29}, 2017 & Timbre-type histograms & HMM  & 0.212 \\
\addlinespace
Sargent et al. \cite{34}, 2011 & MFCCs, chromas & Viterbi  & 0.356 \\
\addlinespace
Ullrich et. al \cite{22}, 2014 & MLS & CNN  & 0.465 \\
\addlinespace
Grill \& Schlüter \cite{4}, 2015 & MLS, SSLMs & CNN  & 0.523 \\
\addlinespace
Grill \& Schlüter \cite{Grill2015MusicAnnotations}, 2015 & MLS, PCPs, SSLMs & CNN  & 0.508 \\
\addlinespace
Hadria \& Peeterss \cite{35}, 2017 & MLS, SSLMs & CNN  & 0.291 \\
\addlinespace
\cite{deepfeaturesegment}, 2019 & CQT & CNN  & \textbf{0.535} \\
\addlinespace
Ours, 2023 & Raw waveforms & CNN  & 0.288 \\
\bottomrule
\end{tabularx}
\caption[Baseline. State-of-the-art table.]{Previous studies' boundary detection f-measure results using unsupervised methods for a 0.5s time-window tolerance. Only the top-performing algorithm for each year on the SALAMI dataset is displayed. This table has been extended from \cite{Hernandez-Olivan2021MusicFeatures}.}
\label{tab:comparison_table}
\end{table}
